### 2024-06-19 texts/paper_closing.tex
new tables after adding t_timeslice/t_timecfg

% Created 2024-05-30 do 10:16
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon May 27 11:25:43 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrll}
  \hline 
 \multicolumn{1}{l}{Self-identification} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Self-ID (recoded)} & \multicolumn{1}{l}{examples}\\ 
 \hline
 Museum & 190 & Museum & Museum Kampa, Museum Barberini \\ 
  Foundation & 104 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
  Collection &  69 & Collection & The Farjam Collection, Sammlung Boros \\ 
  None &  64 & Other & The Bunker, The Broad \\ 
  Center &  17 & Other & Dairy Art Centre, Art Center Nabi \\ 
  Gallery &  14 & Other & Saatchi Gallery, Galerie C15 \\ 
  Art space &  13 & Other & El Espacio 23, Qiao Space \\ 
  House / villa &  11 & Other & Villa La Fleur, Casa Daros Rio \\ 
  Institute &  10 & Other & Instituto Inhotim, Woods Art Institute \\ 
  Kunsthalle &   8 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
  Park / garden &   3 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
   \hline
\end{tabular}
\caption{Selfidentification} 
\label{tbl:t_selfid}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon May 27 11:25:41 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 294 & 0.584 & 0.604 & 0.49 & 0 & 1 \\ 
   & Gender - Female & 79 & 0.157 & 0.166 & 0.37 & 0 & 1 \\ 
   & Gender - Couple & 130 & 0.258 & 0.231 & 0.42 & 0 & 1 \\ 
   & Founder - alive &  &  & 0.903 & 0.30 & 0 & 1 \\ 
   & Founder - died recently &  &  & 0.019 & 0.13 & 0 & 1 \\ 
   & Founder - died 2+ years ago &  &  & 0.079 & 0.27 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 190 & 0.378 & 0.408 & 0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 104 & 0.207 & 0.189 & 0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 69 & 0.137 & 0.130 & 0.34 & 0 & 1 \\ 
   & Self-Identification - Other & 140 & 0.278 & 0.274 & 0.45 & 0 & 1 \\ 
   & Founder name in Museum name & 240 & 0.477 & 0.477 & 0.50 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  & 0.802 & 0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  & 0.144 & 0.35 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  & 0.053 & 0.23 & 0 & 1 \\ 
   & Exhibition any &  &  & 0.630 & 0.48 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  & 0.450 & 1.26 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  & 1.337 & 1.68 & 0.000087 & 10.81 \\ 
   & Nbr PM within 10km &  &  & 1.778 & 3.14 & 0 & 16 \\ 
   & Region - Africa & 8 & 0.016 & 0.012 & 0.11 & 0 & 1 \\ 
   & Region - Asia & 142 & 0.282 & 0.292 & 0.45 & 0 & 1 \\ 
   & Region - Europe & 248 & 0.493 & 0.497 & 0.50 & 0 & 1 \\ 
   & Region - Latin America & 23 & 0.046 & 0.042 & 0.20 & 0 & 1 \\ 
   & Region - North America & 72 & 0.143 & 0.138 & 0.34 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.020 & 0.019 & 0.13 & 0 & 1 \\ 
   & Time Period 2000-2004 &  &  & 0.101 & 0.30 & 0 & 1 \\ 
   & Time Period 2005-2009 &  &  & 0.166 & 0.37 & 0 & 1 \\ 
   & Time Period 2010-2014 &  &  & 0.258 & 0.44 & 0 & 1 \\ 
   & Time Period 2015-2019 &  &  & 0.331 & 0.47 & 0 & 1 \\ 
   & Time Period 2020-2024 &  &  & 0.145 & 0.35 & 0 & 1 \\ 
   & Great Recession (2008/09) &  &  & 0.076 & 0.27 & 0 & 1 \\ 
   & Covid Pandemic (2020/21) &  &  & 0.145 & 0.35 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon May 27 11:25:51 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}D{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4} & \multicolumn{1}{l}{r\_pop4\_woenv}\\ 
 \hline
  \multicolumn{4}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .02 \; (0.34) & .10 \; (0.34) \\ 
   & Gender - Couple & -.10 \; (0.32) & -.15 \; (0.32) \\ 
   & Founder - died recently & 1.09 \; (0.61) & 1.03 \; (0.61) \\ 
   & Founder - died 2+ years ago & -.06 \; (0.55) & -.19 \; (0.56) \\ 
   \multicolumn{4}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .25 \; (0.42) & .44 \; (0.41) \\ 
   & Self-Identification - Collection & -.46 \; (0.54) & .00 \; (0.50) \\ 
   & Self-Identification - Other & 1.12 \; (0.31)^{***} & 1.04 \; (0.30)^{***} \\ 
   & AN Ranking - Included & .25 \; (0.35) & .26 \; (0.35) \\ 
   & AN Ranking - Dropped & .51 \; (0.50) & .52 \; (0.49) \\ 
   & Founder name in Museum name & .09 \; (0.28) & .06 \; (0.28) \\ 
   & Exhibition any & -.22 \; (0.27) & -.22 \; (0.27) \\ 
   \multicolumn{4}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .63 \; (0.35) &  \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) &  \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} &  \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} &  \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} &  \\ 
   & Great Recession (2008/09) & -1.61 \; (1.01) &  \\ 
   & Covid Pandemic (2020/21) & .39 \; (0.29) &  \\ 
   \hline
 & Museum-years & 6096 & 6096 \\ 
   & Closures & 68 & 68 \\ 
   & log. Likelihood & -338.36 & -351.64 \\ 
   & AIC & 712.73 & 725.28 \\ 
   & BIC & 752.68 & 749.69 \\ 
   \hline 
 \multicolumn{4}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

>>>>

% Created 2024-06-19 wo 12:22
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Wed Jun 19 12:18:06 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrll}
  \hline 
 \multicolumn{1}{l}{Self-identification} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Self-ID (recoded)} & \multicolumn{1}{l}{examples}\\ 
 \hline
 Museum & 190 & Museum & Museum Kampa, Museum Barberini \\ 
  Foundation & 104 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
  Collection &  69 & Collection & The Farjam Collection, Sammlung Boros \\ 
  None &  64 & Other & The Bunker, The Broad \\ 
  Center &  17 & Other & Dairy Art Centre, Art Center Nabi \\ 
  Gallery &  14 & Other & Saatchi Gallery, Galerie C15 \\ 
  Art space &  13 & Other & El Espacio 23, Qiao Space \\ 
  House / villa &  11 & Other & Villa La Fleur, Casa Daros Rio \\ 
  Institute &  10 & Other & Instituto Inhotim, Woods Art Institute \\ 
  Kunsthalle &   8 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
  Park / garden &   3 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
   \hline
\end{tabular}
\caption{Selfidentification} 
\label{tbl:t_selfid}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Wed Jun 19 12:18:05 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 294 & 0.584 & 6.0e-01 &  0.49 & 0 & 1 \\ 
   & Gender - Female & 79 & 0.157 & 1.7e-01 &  0.37 & 0 & 1 \\ 
   & Gender - Couple & 130 & 0.258 & 2.3e-01 &  0.42 & 0 & 1 \\ 
   & Founder - alive &  &  & 9.0e-01 &  0.30 & 0 & 1 \\ 
   & Founder - died recently &  &  & 1.9e-02 &  0.13 & 0 & 1 \\ 
   & Founder - died 2+ years ago &  &  & 7.9e-02 &  0.27 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 190 & 0.378 & 4.1e-01 &  0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 104 & 0.207 & 1.9e-01 &  0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 69 & 0.137 & 1.3e-01 &  0.34 & 0 & 1 \\ 
   & Self-Identification - Other & 140 & 0.278 & 2.7e-01 &  0.45 & 0 & 1 \\ 
   & Founder name in Museum name & 240 & 0.477 & 4.8e-01 &  0.50 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  & 8.0e-01 &  0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  & 1.4e-01 &  0.35 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  & 5.3e-02 &  0.23 & 0 & 1 \\ 
   & Exhibition any &  &  & 6.3e-01 &  0.48 & 0 & 1 \\ 
   & Opening year &  &  & 2.0e+03 & 11.10 & 1960 & 2020 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  & 4.5e-01 &  1.26 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  & 1.3e+00 &  1.68 & 0.000087 & 10.81 \\ 
   & Nbr PM within 10km &  &  & 1.8e+00 &  3.14 & 0 & 16 \\ 
   & Region - Africa & 8 & 0.016 & 1.2e-02 &  0.11 & 0 & 1 \\ 
   & Region - Asia & 142 & 0.282 & 2.9e-01 &  0.45 & 0 & 1 \\ 
   & Region - Europe & 248 & 0.493 & 5.0e-01 &  0.50 & 0 & 1 \\ 
   & Region - Latin America & 23 & 0.046 & 4.2e-02 &  0.20 & 0 & 1 \\ 
   & Region - North America & 72 & 0.143 & 1.4e-01 &  0.34 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.020 & 1.9e-02 &  0.13 & 0 & 1 \\ 
   & Time Period 2000-2004 &  &  & 1.0e-01 &  0.30 & 0 & 1 \\ 
   & Time Period 2005-2009 &  &  & 1.7e-01 &  0.37 & 0 & 1 \\ 
   & Time Period 2010-2014 &  &  & 2.6e-01 &  0.44 & 0 & 1 \\ 
   & Time Period 2015-2019 &  &  & 3.3e-01 &  0.47 & 0 & 1 \\ 
   & Time Period 2020-2024 &  &  & 1.4e-01 &  0.35 & 0 & 1 \\ 
   & Great Recession (2008/09) &  &  & 7.6e-02 &  0.27 & 0 & 1 \\ 
   & Covid Pandemic (2020/21) &  &  & 1.4e-01 &  0.35 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Wed Jun 19 12:18:22 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .02 \; (0.34) \\ 
   & Gender - Couple & -.10 \; (0.32) \\ 
   & Founder - died recently & 1.09 \; (0.61) \\ 
   & Founder - died 2+ years ago & -.06 \; (0.55) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .25 \; (0.42) \\ 
   & Self-Identification - Collection & -.46 \; (0.54) \\ 
   & Self-Identification - Other & 1.12 \; (0.31)^{***} \\ 
   & AN Ranking - Included & .25 \; (0.35) \\ 
   & AN Ranking - Dropped & .51 \; (0.50) \\ 
   & Founder name in Museum name & .09 \; (0.28) \\ 
   & Exhibition any & -.22 \; (0.27) \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .63 \; (0.35) \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} \\ 
   & Great Recession (2008/09) & -1.61 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .39 \; (0.29) \\ 
   \hline
 & Museums & 503 \\ 
   & Museum-years & 6096 \\ 
   & Closures & 68 \\ 
   & log. Likelihood & -338.36 \\ 
   & AIC & 712.73 \\ 
   & BIC & 752.68 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}
